Variety in the Implementation of Nonlinear Least Squares Program Codes

### 2022-01-20 VarietyInNLS/VarietyInNonlinearLeastSquaresCodes.Rmd
adjust "Variety"

---
title: "Variety in the Implementation of Nonlinear Least Squares Program Codes"
author: 
   - John C Nash, retired professor, University of Ottawa
date: "16/02/2021"
output: 
    pdf_document:
        keep_tex: false
        toc: true
bibliography: ../BibSupport/ImproveNLS.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## ??require(bookdown) # language engine to display text??
```

@@

>>>>

---
title: "Variety in the Implementation of Nonlinear Least Squares Program Codes"
author: 
   - John C Nash, retired professor, University of Ottawa
date: "16/02/2021 revised 20/01/2022"
output: 
    pdf_document:
        keep_tex: false
        toc: true
bibliography: ../BibSupport/ImproveNLS.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
## require(bookdown) # language engine to display text??
```

@@

# The Problem to be solved

Given a function

where $x$ is a set of real valued parameters, we wish to find the minimum of $f(x)$
with respect to x. There may be additional conditions that add to the complexity of
the problem such as

- bounds (or box) constraints of the form  $$ l_i <= x_i <= u_i $$ alternatively
  written in vector form $$ l <= x <=u $$

- masks (or fixed parameters), for example, $$ x_i = value_i $$. Such constraints
  reduce the dimensionality of the nonlinear least squares problem, and we could
  specify the problem without the masked parameters. However, it is sometimes very
  convenient to be able to write our problem with such paramters that may later be
  altered in value or allowed to vary in an optimization of the sum of squares.

- inequality constraints, which in general may be written as 
  $$ C_k(x) >=0 $$, which can be written as a vector form $$ C(x) >= 0 $$
  A special and important case is that of **linear inequalities** $$ A x >= b $$,
  that is, $$ C(x) = A x - b $$.
